Active Learning from Blackbox to Timed Connectors

### 2016-01-20 paper/paper.tex
.

\begin{itemize}
  \item [-] A \emph{Sync} channel accepts a data item from its source end iff the data item can be
    dispensed through its sink end simultaneously.
  \item [-] A \emph{LossySync} channel is always ready to accept data items. These items will be
    dispensed through its sink end simultaneously if possible, otherwise they will be lost.
  \item [-] A \emph{SyncDrain} channel has two source ends and no sink end. It can accept a data
    item through one of its source end iff a data item is also available to be accepted
    simultaneously through the other end. Then both items will be dropped.
  \item [-] A \emph{FIFO1} channel is an asychronous channel with a buffer cell. It accepts a
    data item whenever the buffer is empty. 
  \item [-] A t-timer channel accepts any data item from its source end, and later dispense it to
    its sink end after a delay of $t$ time units.
    \footnote{Here the interpretation of t-Timer is a bit different as in other works like
    \cite{DBLP:conf/sefm/ArbabBBR04, DBLP:conf/tase/Meng12}, but we can easily transform between the
    two kinds of behavior by composing with some other basic channels.}
\end{itemize}

@@

\subsection{Counter-Examples' Analysis} 
Apparently, the closed hypothesis presented in Figure \ref{fig:hypo2} is not the 2-Timer
channel. It's easy to find a counter-example $s_0=a,\rnoread-T-T-\bot,\rread$ where $mq(s)=a$ while
according to the hypothesis, the result shoud have been $\rempty$. In this section, we show how to
find and analyze counter-examples using the method in \cite{DBLP:conf/sfm/SteffenHM11}.

Firstly, we give a formal definition of \emph{counter-examples}. With a observation table $obs$ and
a sequence $s$, we use $hq(obs,s)$ to denote the execution result of $obs$ under the input sequence
$s$. Obviously we have $hq(obs,s) = mq(acc(s')a)$ where $a$ is the last element of $s$ and $s=s'a$.

\begin{definition}[Counter-Example]
  sequence $s$ is called a counter-example of $obs$ iff $mq(s)\neq hq(obs,s)$.
\end{definition}

Now we consider the reason that lead to existance of counter examples. Since
the suffix set $D$ is used to distinguish different states, the existance of counter-examples
shows that the current suffix set $D$ is not powerful enough to distinguish all different states.

Considering a counter example $s$, we define the function MaxSuffix($s,obs$) as
\[
\max\{d\in\mathcal{I}^+|s=s'd, mq(acc(s',obs.D)d)\neq mq(s)\}
\]
After appending $d$ in $D$, we can rebuild a closed hypothesis where $s$ is no longer a
counter-example.

The whole L* algorithm can be concluded as follows.
\begin{algorithm} 
  \caption{L*} 
  \label{alg:lstar}
  \KwIn{Oracle interface $mq,eq$, Input actions $\mathcal{I}$}
  \KwOut{Observation table $obs$} 
  $obs.S$ initialized as empty\;
  $obs.D$ initialized as $\{\{i\}|i\in\mathcal{I}\}$\;
  \Repeat{$ce=true$}{
    $obs$ = CloseTable($mq$, $\mathcal{I}$, $D$)\;
    $ce=eq(obs)$\;
    \If {$ce!=true$} {
      D.append(MaxSuffix(s))\;
    }
  }
  \Return $obs$\; 
\end{algorithm}

>>>>

\begin{itemize}
  \item [-] A \emph{Sync} channel accepts a data item from its source end iff the data item can be
    dispensed through its sink end simultaneously.
  \item [-] A \emph{LossySync} channel is always ready to accept data items. These items will be
    dispensed through its sink end simultaneously if possible, otherwise they will be lost.
  \item [-] A \emph{SyncDrain} channel has two source ends and no sink end. It can accept a data
    item through one of its source end iff a data item is also available to be accepted
    simultaneously through the other end. Then both items will be dropped.
  \item [-] A \emph{FIFO1} channel is an asychronous channel with a buffer cell. It accepts a
    data item whenever the buffer is empty. 
  \item [-] A t-timer channel accepts any data item from its source end, and later dispense it to
    its sink end after a delay of $t$ time units.
    \begin{footnote}
      Here the interpretation of t-Timer is a bit different as in other works like
      \cite{DBLP:conf/sefm/ArbabBBR04, DBLP:conf/tase/Meng12}, but we can easily transform between the
      two kinds of behavior by composing with some other basic channels.
    \end{footnote}
\end{itemize}

@@

\subsection{Counter Examples' Analysis} 
Apparently, the closed hypothesis presented in Figure \ref{fig:hypo2} is different with the 2-Timer
channel. It's easy to find a counter-example $s_0=a,\rnoread-T-T-\bot,\rread$ where $mq(s)=a$ while
according to the hypothesis, the result should be $\rempty$. In this section, we show how to
find and analyze counter-examples using the method in \cite{DBLP:conf/sfm/SteffenHM11}.

Firstly, we give a formal definition of \emph{counter examples}. With a observation table $obs$ and
a sequence $s$, we use $hq(obs,s)$ to denote the execution result of its corresponding hypothesis
$\mathcal{H}$ under the input sequence
$s$. Obviously we have $hq(obs,s) = mq(acc(s')a)$ where $s=s'a,a\in\mathcal{I}$.

\begin{definition}[Counter Example]
  an input sequence $s$ is a counter example of $obs$ iff $mq(s)\neq hq(obs,s)$.
\end{definition}

Now we consider the reason that lead to existance of counter examples. Since
the suffix set $D$ is used to distinguish states, the existance of counter-examples
shows that the current suffix set $D$ is not powerful enough to recognize the uncovered states in
$next$ (see in Algorithm \ref{alg:buildtable}).

Considering a counter example $s$, we need a new suffix to distinguish the uncovered states, which
can be calculated by Suffix($s,obs$):
\[
\max\{d\in\mathcal{I}^+|s=s'd, mq(acc(s',obs.D)d)\neq mq(s)\}
\]
After appending $d$ in $D$, we can prove that at least one new state will be found.

\begin{theorem}
\end{theorem}

The whole L* algorithm can be concluded as follows.
\begin{algorithm} 
  \caption{L*} 
  \label{alg:lstar}
  \KwIn{Oracle interface $mq,eq$, Input actions $\mathcal{I}$}
  \KwOut{Observation table $obs$} 
  $obs.S$ initialized as empty\;
  $obs.D$ initialized as $\{\{i\}|i\in\mathcal{I}\}$\;
  \Repeat{$ce=true$}{
    $obs$ = CloseTable($mq$, $\mathcal{I}$, $obs$)\;
    $ce=eq(obs)$\;
    \If {$ce\neq true$} {
      D.append(Suffix(s))\;
    }
  }
  \Return $obs$\; 
\end{algorithm}
